A holographic approach to the six-dimensional superconformal index

### 2022-10-13 fivebranes/index.tex
small edits

We will consider the eleven-dimensional theory on eleven-manifolds that arise as total spaces of vector bundles. Placing the theory in the backreacted geometry is a 2-step procedure:

\begin{itemize}
  \item Place the eleven-dimensional theory on the complement of the zero section. To do so, we will wish to describe the complement of the zero-section in a way that facilitates natural operations on holomorphic-topological local $L_{\infty}$-algebras.

@@

Consider the bundle $\R\oplus W$; this bundle has a canonical partially flat connection. We wish to consider our eleven dimensional model on $M = Tot (\R\oplus W)$ which is the total space of the \textit{real} rank five bundle $\R\oplus W$ over $Z$. The partially flat connection on $\R\oplus W$ equips $M$ with a canonical THF structure $F_{M}\subset T_{M}^{\C}$.

We place a stack of $N$ fivebranes wrapping the zero section in $\R\oplus W$.
Denote the complement of the zero section by
\[
\mathring{M} = \text{Tot}(\R\oplus W) - 0(Z).
\]

We may choose fiber coordinates of the bundle $t, w_{1}, w_{2}$ of $\R \oplus W$ over $Z$ and a fiberwise partially hermitian metric.

Explicitly, the corresponding norm defines a map
\begin{align*}
 h \colon  M & \to \R_{+} \\
  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
\end{align*}
Letting $\pi \colon M \to Z$ be the natural projection, we obtain the projection
\[
p \define (h,\pi) \colon M \to \R_{+}\times Z
\]
which restricts to an $S^4$ bundle $p|\mathring {M} \colon \mathring{M} \to \R_{>0} \times Z$.
These embeddings and projections fit inside of the following commutative diagram
\[
\begin{tikzcd}
\mathring{M} \ar[d,"p|\mathring M"'] \ar[r,hook] & M \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
\R_{>0} \times Z \ar[r,hook] & \R_{+} \times Z & \ar[l,hook',"0 \times \id"] Z.
\end{tikzcd}
\]
The inclusions on the left are the natural embeddings.
The top right inclusion is the zero section of $M = {\rm Tot}(\R \oplus V)$ and the bottom right inclusion is the embedding at radius $r = 0$.

As we elaborated in section \ref{s:thfmflds}, the eleven-dimensional theory is defined on the THF manifold $\mathring M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $\mathring M$. Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|\mathring M$. The resulting sheaf of $L_\infty$ algebras $(p|\mathring M)_*\cL_{sugra}$ describes, in the BV formalism, the compactified theory on the seven-manifold $\R_{>0} \times Z$.

@@

The existence of a partially flat connection amounts to a choice of splitting \[\sigma: \pi^{*}T^{0,1}_{Z}\to F_{M}\] of the top row. Both $F_{M}$ and $\pi^{*}T^{1,0}_{Z}$ are involutive, and the flatness of the connection implies that $\sigma$ preserves the lie brackets on sections.

@@

Explicitly, we set
\[
  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} & = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}
\]
for the complex resoling functions on $\mathring M$ constant in the directions of $F_{\mathing M}$ that are tangent to the fibers of $(p|\mathring M)$.

Likewise, we let
\[
  F_{\R_{>0}\times Z} = T_{\R_{>0}}\oplus T^{0,1}_{Z}
\] be the subbundle of the tangent bundle of the base locally spanned by $\del_{}t, \del_{z_{i}}$ and $(p|\mathring M)^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}$ the pullback, which is a subbundle of $T_{\mathring M}$. We will let $\cA^{\bu}_{\R_{>0}\times Z}&  = \cA^{\bu}_{F _{\R_{>0}\times Z}}$ denote the THF complex resolving functions constant along the elaves of this foliation on the base.

@@

We first note that the splitting gives us an isomorphism of $C^{\infty}_{\mathring M}$-modules
\begin{align*}
  \cA^{\bu}_{\mathring M}(L) & \cong \cA^{\bu}_{(p|\mathring M)^{*}F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\

                         & \cong (p|\mathring M)^{*}\cA ^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\

\end{align*}

where we have just used that pullback commutes with taking the exterior power. Here, the tensor product is take in $C^{\infty}_{\mathing M}$-modules.

@@

 The left hand side of the above isomorphism has a canonical $\cA ^{#}_{\R_{>0}\times Z}$-modules structure. It remains to discuss compatibility with the differential along the base. The compatibility condition is expressed through the observation that the pro-vector bundle \[(p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\] will have the structure of a partial flat connection defined along the leaves of $F_{\R_{>0}\times Z}$. We can construct such a connection from analyzing the behavior of the THF differential $\thfd$ under the splitting.

@@

\[\thfd_{i} :  (p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \to \cA^{i}_{\R_{\geq >0} \times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M)_{*} \cA^{\bullet-i+1}_{\mathring M/\R_{>0}\times Z}(L).\]

@@

\begin{prop}\label{p:dimred}
  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
  \beqn
  \cA^\bu_{\R_{>0}\times Z}\otimes \mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)
  \eeqn

  with the $\cA^{\bullet}_{\R_{>0}\times Z}$-module structure coming from the partial flat connection induced by $\thfd_{1}$.
\end{prop}

@@

In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where
\beqn
M = Tot (\R\oplus \C^{2}\to \C^{3}), \ \ \ \ \ \ \mathring M = \R\times \C^2\times \C^3 \setminus (0 \times \C^3).
\eeqn
In this case, the above spectral sequence clearly degenerates at the $E_{2}$-page.

>>>>

We will consider the eleven-dimensional theory on eleven-manifolds that arise as total spaces of vector bundles. Placing the theory in the backreacted geometry is a two step procedure:

\begin{itemize}
  \item Place the eleven-dimensional theory on the complement of the zero section. 
  To do so, we will wish to describe the complement of the zero-section in a way that facilitates a description of the perturbative theory in terms of natural operations on holomorphic-topological local $L_{\infty}$-algebras.

@@

Consider the bundle $\R\oplus W$; this bundle has a canonical partially flat connection. We wish to consider our eleven dimensional model on $M = \text{Tot} (\R\oplus W)$ which is the total space of the \textit{real} rank five bundle $\R\oplus W$ over $Z$. The partially flat connection on $\R\oplus W$ equips $M$ with a canonical THF structure $F_{M}\subset T_{M}^{\C}$.

We place a stack of $N$ fivebranes wrapping the zero section in $\R\oplus W$.
Denote the complement of the zero section by
\[
\mathring{M} = \text{Tot}(\R\oplus W) - 0(Z).
\]
We choose fiber coordinates of the bundle $t, w_{1}, w_{2}$ of $\R \oplus W$ over $Z$ and a fiberwise partially hermitian metric.
The corresponding norm defines a map
\begin{align*}
 h \colon  M & \to \R_{+} \\
  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
\end{align*}
Letting $\pi \colon M \to Z$ be the natural projection, we obtain the projection
\[
p \define (h,\pi) \colon M \to \R_{+}\times Z
\]
which restricts to an $S^4$ bundle $p|\mathring {M} \colon \mathring{M} \to \R_{>0} \times Z$.
These embeddings and projections fit inside of the following commutative diagram
\[
\begin{tikzcd}
\mathring{M} \ar[d,"p|\mathring M"'] \ar[r,hook] & M \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
\R_{>0} \times Z \ar[r,hook] & \R_{+} \times Z & \ar[l,hook',"0 \times \id"] Z.
\end{tikzcd}
\]
The inclusions on the left are the natural embeddings.
The top right inclusion is the zero section of $M = {\rm Tot}(\R \oplus V)$ and the bottom right inclusion is the embedding at radius $r = 0$.

As we elaborated in \S \ref{s:thfmflds}, the eleven-dimensional theory is defined on the THF manifold $\mathring M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $\mathring M$. Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|\mathring M$. The resulting sheaf of $L_\infty$ algebras $(p|\mathring M)_*\cL_{sugra}$ describes, in the BV formalism, the compactified theory on the seven-manifold $\R_{>0} \times Z$.

@@

The existence of a partially flat connection amounts to a choice of splitting \[\sigma \colon \pi^{*}T^{0,1}_{Z}\to F_{M}\] of the top row. Both $F_{M}$ and $\pi^{*}T^{1,0}_{Z}$ are involutive, and the flatness of the connection implies that $\sigma$ preserves the lie brackets on sections.

@@

Explicitly, we set
\[
  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}
\]
for the complex resoling functions on $\mathring M$ constant in the directions of $F_{\mathring M}$ that are tangent to the fibers of $(p|\mathring M)$.

Likewise, we let
\[
  F_{\R_{>0}\times Z} = T_{\R_{>0}}\oplus T^{0,1}_{Z}
\] 
be the subbundle of the tangent bundle of the base locally spanned by $\del_{}t, \del_{z_{i}}$ and $(p|\mathring M)^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}$ the pullback, which is a subbundle of $T_{\mathring M}$. We will let $\cA^{\bu}_{\R_{>0}\times Z} = \cA^{\bu}_{F _{\R_{>0}\times Z}}$ denote the THF complex resolving functions constant along the elaves of this foliation on the base.

@@

We first note that the splitting gives us an isomorphism of $C^{\infty}_{\mathring M}$-modules
\begin{align*}
  \cA^{\bu}_{\mathring M}(L) & \cong \cA^{\bu}_{(p|\mathring M)^{*}F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\
                         & \cong (p|\mathring M)^{*}\cA ^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\
\end{align*}
where we have used the fact that pullback commutes with taking the exterior power. Here, the tensor product is take in $C^{\infty}_{\mathring M}$-modules.

@@

The left hand side of the above isomorphism has a canonical $\cA ^{\#}_{\R_{>0}\times Z}$-module structure. 
It remains to discuss compatibility with the differential along the base. The compatibility condition is expressed through the observation that the pro-vector bundle \[(p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\] will have the structure of a partial flat connection defined along the leaves of $F_{\R_{>0}\times Z}$. We can construct such a connection from analyzing the behavior of the THF differential $\thfd$ under the splitting.

@@

\[\thfd_{i} \colon  (p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \to \cA^{i}_{\R_{\geq >0} \times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M)_{*} \cA^{\bullet-i+1}_{\mathring M/\R_{>0}\times Z}(L).\]

@@

\begin{prop}\label{p:dimred}
  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
  \beqn
  \cA^\bu_{\R_{>0}\times Z}\otimes \mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)
  \eeqn
with the $\cA^{\bullet}_{\R_{>0}\times Z}$-module structure coming from the partial flat connection induced by $\thfd_{1}$.
\end{prop}

@@

In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where
\beqn
M = \text{Tot} (\R\oplus \C^{2}\to \C^{3}), \ \ \ \ \ \ \mathring M = \R\times \C^2\times \C^3 - (0 \times \C^3).
\eeqn
In this case, the above spectral sequence clearly degenerates at the $E_{2}$-page.
